A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-04 1_intro.tex
fix max bead width deviation in Jin

The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS},
which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a homogeneity assumption.
Therefore, a narrower range of widths is desirable.

>>>>

The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of \revise{$2$}{$3.2$}~\cite{Jin2017JMS},
% (0.8 * 2) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a homogeneity assumption.
Therefore, a narrower range of widths is desirable.
